---
title: "Working sessions"
---

### Join our R working sessions in Grenoble

Each month, we will organize one working session of 2 hours (on thursdays, from 16h-18h, at the [IMAG building](https://r-in-grenoble.github.io/members.html)). 

Please find the guidelines for these sessions:
    
- Everyone is welcome (beginners to advanced R users, just bring your laptop).

- Presentations/tutorials will last 30 to 60 min, on some R topics that can be useful to many people, with practical examples.

- During the second part of the session, people could ask and answer some questions about specific problems they encounter when coding in R.

- During this time, beers and sodas will be offered by [the Grenoble Alpes Data Institute](https://data-institute.univ-grenoble-alpes.fr/).

- If you wish to share your R experience during a working session and/or to co-animate a working session, please [contact us](mailto:florian.prive@univ-grenoble-alpes.fr,magali.richard@univ-grenoble-alpes.fr).

### Schedule

*Click on the title to see the session description*

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
Sys.setlocale("LC_TIME", "C")
library(htmltools)
```

```{r, warning=FALSE}
program <- tribble(
  ~Date, ~Session, ~Title, ~Description, ~Authors,
  "28/09/2017", "1/10", "Introduction to R", "wait for it...", "F. Chuffart & F. Boyer",
  "19/10/2017", "2/10","ggplot2", "You all know the package ggplot2 from Hadley Wickham. It is reputed to make nice plots that could be used in publications, for example. It is also reputed to be hard to begin with or to customize. We will explain the reasoning behind ggplot2 and the use of tidy data which is important to understand in order to master ggplot2. We will also show the common problems an R user could face when using ggplot2 (and their solutions). There will be a lot of nice plots :-)", "F. Privé & K. Caye",
  "16/11/2017", "3/10", "igraph", "wait for it...", "A. Achard & ...",
  "14/12/2017", "4/10", "Geographical Information Systems", "wait for it...", "F. Boyer & ...",
  "18/01/2018", "5/10", "RStudio and git", "RStudio is an integrated development environment (IDE) that facilitate the life of R users. We will show some of the tools that are provided by the RStudio IDE that could help you save some precious time and effort. Two of these tools are the integration of Git and the R projects. We will see in particular how these two tools are integrated in RStudio and how much is it important to work with them. Make sure you have the latest version of RStudio and git installed (https://support.rstudio.com/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN).", "F. Privé & M. Richard",
  "08/02/2018", "6/10", "Best coding practices", "wait for it...", "A. Arnaud & ...",
  "15/03/2018", "7/10", "Rcpp", "Your code isn't fast enough? We will see how to make simple Rcpp code to accelerate your code. We will see that Rcpp is useful for loops, for avoiding copies, etc. We will also see that Rcpp isn't always faster than an optimized R code. Finally, we will see how to integrate some Rcpp code to your packages and notebooks.", "F. Privé & A. Arnaud",
  "26/04/2018", "8/10", "Parallel computing", "wait for it...", "F. Chuffart & L. Viry",
  "24/05/2018", "9/10", "Big Memory", "In this session, we will talk about the two packages bigmemory and bigstatsr. The package bigmemory provides a special class of matrix than can be used to store some data in a matrix-like format on your disk but to access it almost as if it were in memory. It is particularly useful is you have a large matrix to analyze but not enough RAM on your computer. We will then see the statistical and helper functions that are provided by the package bigstatsr for this kind of matrices.", "F. Privé & ...",
  "14/06/2018", "10/10", "Make your personal weboage with R", "You know nothing about web development? Me neither (at least when I came up with this solution). In this session, you will learn how to make your personal website with only R code in only a few minutes. For example, the site of our group is made with this R solution.", "F. Privé & M. Richard"
) %>%
  mutate(Date = dmy(Date)) 

stopifnot(all(wday(program$Date) == 5)) # Thursdays (begin with Sundays)
          
program <- program %>%
  arrange(Date) %>%
  mutate(Date = format(Date, format = "%B %d, %Y"))
```


```{css}
.schedule {
  display: flex;
  justify-content: space-between;
  flex-wrap: wrap;
}

.limit {
  width: 100%;
  padding: 5px 0 5px 0;
}

.workshops-button {
  padding: 0.75em 1.25em;
  background-color: #cccccc;
  opacity: 0.9;
  width: auto;
  color: black;
  text-align: center;
  overflow: auto;
}

.left-date {
  width: 20%;
  float: left;
  text-align: left;
}

.center-title {
  width: 60%;
  float: left;
  text-align: center;
}

.right-authors {
  width: 20%;
  float: right;
  text-align: right;
}

.workshops {
  margin: 1em 0;
}

.active {
  background-color: #333333;
  color: whitesmoke;
}
```

```{js}
function main() {
  $('.schedule').hide();
  $('.schedule').fadeIn(2000);
  $('.workshops').hide();
  $('.workshops-button').on('click', function() {
    $(this).next().slideToggle(400);
    $(this).toggleClass('active');
  });
}
 
$(document).ready(main);
```


```{r}
div(
  class = "schedule",
  apply(program, 1, function(event) {
    div(
      class = "limit",
      div(class = "workshops-button", 
          div(class = "left-date", 
              event[['Date']]),
          div(class = "center-title", 
              tags$i(event[['Title']])),
          div(class = "right-authors",
              event[['Authors']])),
      tags$ul(class = "workshops",
              event[["Description"]])
    )
  })
) 
```

