---
title: "About our team"
editor_options:
  chunk_output_type: console
---

```{r package, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(sp)
library(leaflet)
library(DT)
library(gt)
library(tidyverse)
```

```{r input members}
# create a table

members <- data.frame(
  Grade = c("PI"),
  `名前` = c("堤田 成政"),
  Name = c("Narumasa Tsutsumida"),
  #Keywords = c("地理情報科学(GISci), 地理情報システム(GIS), リモートセンシング(Remote Sensing), 空間モデリング(Spatial modeling), ジオデータサイエンス(Geo Data Science)"),
  link = c("https://narutstsmd.wordpress.com")
)

```

<br>

## メンバー
##  Members
```{r gt name list datatable, eval=F}
# display table
datatable(select(members, c(名前, NameE, Grade, link)), colnames = c("名前", "Name", "Grade","link"),
              rownames = FALSE, escape = FALSE)
```

<br>

```{r display name list datatable, eval=F}
# display table
members %>% 
    mutate(
        link = map(link, ~ htmltools::a(href = .x, "website")),
        link = map(link, ~ gt::html(as.character(.x)))) %>%
    #gt(.,rowname_col = "Grade")
  gt()
```

### 堤田　成政
### Narumasa Tsutsumida
PI, 准教授  
[National Geographic Fellow](https://www.nationalgeographic.org/find-explorers/narumasa-tsutsumida)  
[OSGeo Charter member](https://wiki.osgeo.org/wiki/User:Naru)  

- [研究者総覧](http://s-read.saitama-u.ac.jp/researchers/pages/researcher/spZMMhAo)
- [Google Scholar](https://scholar.google.co.jp/citations?user=_Hw3vQQAAAAJ)
- [ORCID](https://orcid.org/0000-0002-6333-0301)



<br>

## 所属
## Affiliation

- [埼玉大学大学院理工学研究科数理電子情報部門情報領域](http://www.ics.saitama-u.ac.jp)
- [Department of Information and Computer Sciences, Graduate School of Science and Engineering, Saitama University, Japan](http://www.ics.saitama-u.ac.jp/en/)


<br>


## 住所
## Address

- 〒338-8570 さいたま市桜区下大久保255 埼玉大学　理工学研究科 総合研究棟1号館704・707
- 255 Shimo-Okubo, Sakura ward, Saitama city, Saitama, Room 704・707, Research Building No.1, Department of Information and Computer sciences, Graduate school of Science & Engineering, Saitama University,  Japan, 338-8570


# Where are we?



```{r leaflet map, message=FALSE}
# display map
suppressWarnings(
  leaflet(sp::SpatialPoints(matrix(c(139.60755, 35.86289),nrow = 1)) , width = "100%") %>% 
    setView(lng = 139.60755, lat = 35.86289, zoom = 15) %>% 
    addTiles(options = providerTileOptions(minZoom = 2, maxZoom = 19)) %>%
    addAwesomeMarkers(lng = 139.60755, lat = 35.86289, 
                      popup = "VJ74+3X",
                      label = "VJ74+3X",
                      icon = makeAwesomeIcon("android-locate", library = "ion", markerColor = "red"))  %>%
    htmlwidgets::onRender('
      function(el, x) {
        var myMap = this;
        myMap.on("click", function(e) {
          alert("Latitude: " + e.latlng.lat + "\\nLongitude: " + e.latlng.lng)
        })
      }')
)
```

<br>  

## Coordinates
- (139.60755, 35.86289)
- VJ74+3X
