---
title: "About our team"
editor_options:
  chunk_output_type: console
---

## Where are we?

```{r package, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(sp)
library(leaflet)
library(DT)
```


```{r leaflet map, message=FALSE}
# display map
suppressWarnings(
  leaflet(sp::SpatialPoints(matrix(c(139.60755, 35.86289),nrow = 1)) , width = "100%") %>% 
    setView(lng = 139.60755, lat = 35.86289, zoom = 15) %>% 
    addTiles(options = providerTileOptions(minZoom = 2, maxZoom = 19)) %>%
    addAwesomeMarkers(lng = 139.60755, lat = 35.86289, 
                      popup = "VJ74+3X",
                      label = "VJ74+3X",
                      icon = makeAwesomeIcon("android-locate", library = "ion", markerColor = "red"))  %>%
    htmlwidgets::onRender('
      function(el, x) {
        var myMap = this;
        myMap.on("click", function(e) {
          alert("Latitude: " + e.latlng.lat + "\\nLongitude: " + e.latlng.lng)
        })
      }')
)
```

```{r input members}
# create a table

members <- data.frame(
  NameJ = c("堤田 成政"),
  NameE = c("Narumasa Tsutsumida"),
  Grade = c("Assoc. Prof."),
  Keywords = c("地理情報科学(GISci), 地理情報システム(GIS), リモートセンシング(Remote Sensing), 空間モデリング(Spatial modeling), ジオデータサイエンス(Geo Data Science)")
)

```

<br>

### メンバー (Members)
```{r display name list}
# display table
datatable(select(members, c(NameJ, NameE, Grade, Keywords)), colnames = c("名前", "Name", "Grade", "Keywords"),
              rownames = FALSE, escape = FALSE)
```

<br>

### 所属 (Affiliation)

- [埼玉大学大学院理工学研究科数理電子情報部門情報領域](http://www.ics.saitama-u.ac.jp)
- [Department of Information and Computer Sciences, Graduate School of Science and Engineering, Saitama University, Japan](http://www.ics.saitama-u.ac.jp/en/)


<br>

<!---
Please fill the [google doc](https://docs.google.com/spreadsheets/d/1qdG7PPlRCAU8L6Hhq1D2zT0q9LWDUzBfq7mIzz_6Dm8/edit?usp=sharing) (**follow the guidelines!!**) and wait for an admin to upload your data to the actual list of members.
--->

### 住所(Address)

- 〒338-8570 さいたま市桜区下大久保255 埼玉大学　理工学研究科 総合研究棟1号館
- 255 Shimo-Okubo, Sakura ward, Saitama city, Saitama, Room 707, Research Building No.1, Department of Information and Computer sciences, Graduate school of Science & Engineering, Saitama University,  Japan, 338-8570
