---
title: "About our team"
editor_options:
  chunk_output_type: console
leafletmap: yes
always_allow_html: yes
---

```{r package, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(sp)
library(leaflet)
```


<br>

## メンバー
##  Members

**堤田　成政**  
**Narumasa Tsutsumida**  
PI, 准教授  
PI, Associate Professor 

[National Geographic Fellow](https://www.nationalgeographic.org/find-explorers/narumasa-tsutsumida)  
[OSGeo Charter member](https://wiki.osgeo.org/wiki/User:Naru)  

- [研究者総覧](http://s-read.saitama-u.ac.jp/researchers/pages/researcher/spZMMhAo)
- [Google Scholar](https://scholar.google.co.jp/citations?user=_Hw3vQQAAAAJ)
- [ORCID](https://orcid.org/0000-0002-6333-0301)
- [English HP](https://narutstsmd.wordpress.com)    

　　
<br>
<br>  

**事務補佐員 1名**  
**One administrative staff**  

<br>  

- **D1  1名**  
- **M2  2名**  
- **M1  1名**  
**Four graduate students**


- **B4  5名**  
**Five undergraduate students**



<br>

## 所属
## Affiliation

[埼玉大学大学院理工学研究科数理電子情報部門情報領域](http://www.ics.saitama-u.ac.jp)  
[Department of Information and Computer Sciences, Graduate School of Science and Engineering, Saitama University, Japan](http://www.ics.saitama-u.ac.jp/en/)

[埼玉大学レジリエント社会研究センター](http://iirs.saitama-u.ac.jp/) 兼任  
[International Institute for Resillient Society, Saitama University](http://iirs.saitama-u.ac.jp/en/index.html)
<br>


## 住所
## Address

〒338-8570 さいたま市桜区下大久保255 埼玉大学　理工学研究科 総合研究棟1号館704・707  
255 Shimo-Okubo, Sakura ward, Saitama city, Saitama, Room 704・707, Research Building No.1, Department of Information and Computer sciences, Graduate school of Science & Engineering, Saitama University,  Japan, 338-8570


# Where are we?



```{r leaflet map, message=FALSE}
# display map
suppressWarnings(
  leaflet(sp::SpatialPoints(matrix(c(139.6075469061112, 35.86271761195589),nrow = 1)) , width = "100%") %>% 
    setView(lng = 139.6075469061112, lat = 35.86271761195589, zoom = 15) %>% 
    addTiles(options = providerTileOptions(minZoom = 2, maxZoom = 19)) %>%
    addAwesomeMarkers(lng = 139.6075469061112, lat = 35.86271761195589, 
                      popup = "VJ74+3X",
                      label = "VJ74+3X",
                      icon = makeAwesomeIcon("android-locate", library = "ion", markerColor = "red"))  %>%
    htmlwidgets::onRender('
      function(el, x) {
        var myMap = this;
        myMap.on("click", function(e) {
          alert("Latitude: " + e.latlng.lat + "\\nLongitude: " + e.latlng.lng)
        })
      }')
)
```

<br>  

## Coordinates
- (139.60755, 35.86289)
- VJ74+3X

<br>

## Location link
- [Google maps](https://goo.gl/maps/n8XZ7kf1R8eR4GHk7)

- [Mapion](https://www.mapion.co.jp/m2/35.86271761195589,139.6075469061112,18)

- [Yahoo](https://yahoo.jp/WqUb6x)

