---
title: "Working sessions"
---

Make sure to subscribe to the [r-in-grenoble newsletter](https://listes.univ-grenoble-alpes.fr/sympa/subscribe/r-in-grenoble?previous_action=info) to know when you can register to the next session.

**10 sessions are planned next year, starting in September. We will update the website during the summer. Stay tuned.**

<!-- You can register to session 10 about how to make your personal webpage with R [there](https://www.eventbrite.fr/e/billets-grenoble-rug-working-session-n10-make-your-personal-webpage-with-r-46708386040). -->

Attendance is totally free but registration is mandatory and is on a first come first serve basis.

### Help us communicate

Please talk about our R group with your colleagues. 
<!-- You can also print [this poster](poster.pdf) and put it up somewhere at work. -->

### Join our R working sessions in Grenoble

Each month, we will organize one working session of 2 hours (on thursdays, from 16h-18h, at the [IMAG building](https://r-in-grenoble.github.io/members.html)). 

Please find the guidelines for these sessions:
    
- Everyone is welcome (beginners to advanced R users, just bring your laptop).

- Presentations/tutorials will last 30 to 60 min, on some R topics that can be useful to many people, with practical examples.

- We want to have a lightning talk (5 min) after the main session so that people can quickly present how they use R in their work (or a specific package, etc.).

- During the second part of the session, people could ask and answer some questions about specific problems they encounter when coding in R.

- During this time, food and sodas will be offered by [the Grenoble Alpes Data Institute](https://data-institute.univ-grenoble-alpes.fr/).

- If you wish to share your R experience during a working session and/or to co-animate a working session, please [contact us](mailto:florian.prive@univ-grenoble-alpes.fr,magali.richard@univ-grenoble-alpes.fr).

### Schedule of 2018-2019

*Click on the title to see the session description*

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
Sys.setlocale("LC_TIME", "C")
library(htmltools)
```

```{r, warning=FALSE}
program <- tribble(
  
  ~Date, ~Session, ~Title, ~Description, ~Authors,
  
  "13/09/2018", "1/10", "What R can do for you?", "TODO", "F. Privé & team",
  
  "11/10/2018", "2/10", "Image processing with package {imager}", "TODO", "S. Barthelmé",
  
  "15/11/2018", "3/10", "lm & glm (statistics)", "TODO", "M. Blum & ?",
  
  "06/12/2018", "4/10", "Manage your workflow with package {drake}", "TODO", "X. Laviron & ?",
  
  "31/01/2019", "5/10", "Deep Learning with package {tensorflow}", "TODO", "O. François & ?",
  
  "14/02/2019", "6/10", "Machine Learning with package {caret}", "TODO", "? & ?",

  "14/03/2019", "7/10", "Best coding practices", "TODO", "M. Richard & ?",
  
  "11/04/2019", "8/10", "R Markdown", "TODO", "M. Crispino & J. Arbel",

  "16/05/2019", "9/10", "Data manipulation with package {dplyr}", "TODO", "M. Blum & ?",

  "13/06/2019", "10/10", "Data vizualisation with package {ggplot2}", "TODO", "? & F. Privé"

) %>%
  mutate(Date = dmy(Date)) 

stopifnot(all(wday(program$Date) == 5)) # Thursdays (begin with Sundays)
          
program <- program %>%
  arrange(Date) %>%
  mutate(Date = format(Date, format = "%B %d, %Y"))
```


```{css}
.schedule {
  display: flex;
  justify-content: space-between;
  flex-wrap: wrap;
}

.limit {
  width: 100%;
  padding: 5px 0 5px 0;
}

.workshops-button {
  padding: 0.75em 1.25em;
  background-color: #cccccc;
  opacity: 0.9;
  width: auto;
  color: black;
  text-align: center;
  overflow: auto;
}

.left-date {
  width: 20%;
  float: left;
  text-align: left;
}

.center-title {
  width: 60%;
  float: left;
  text-align: center;
  font-size: 120%;
}

.right-authors {
  width: 20%;
  float: right;
  text-align: right;
}

.workshops {
  margin: 1em 1em 0 0;
}

.active {
  background-color: #333333;
  color: whitesmoke;
}
```

```{js}
function main() {
  $('.schedule').hide();
  $('.schedule').fadeIn(2000);
  $('.workshops').hide();
  $('.workshops-button').on('click', function() {
    $(this).next().slideToggle(400);
    $(this).toggleClass('active');
  });
}
 
$(document).ready(main);
```


```{r}
div(
  class = "schedule",
  apply(program, 1, function(event) {
    div(
      class = "limit",
      div(class = "workshops-button", 
          div(class = "left-date", 
              event[['Date']]),
          div(class = "center-title", 
              tags$i(event[['Title']])),
          div(class = "right-authors",
              event[['Authors']])),
      tags$ul(class = "workshops",
              event[["Description"]])
    )
  })
) 
```

<br>

### Materials from previous sessions

- [Make your personal webpage with R](https://privefl.github.io/R-presentation/rmarkdown-websites.html)

- [Out-of-memory matrices](https://privefl.github.io/R-presentation/bigstatsr.html)

- [Parallel computing](session-parallel.zip)

- [{Rcpp}](https://privefl.github.io/R-presentation/Rcpp.html)

- [Best coding practices](https://jarbel.github.io/Rgoodpractice/rpresentation.html)

- [RStudio and Git](https://privefl.github.io/R-presentation/rstudio-git.html)

- [Geographical Information Systems](http://www-leca.ujf-grenoble.fr/pageperso/boyerfr/ESPACE-PERSO/TP.zip)

- [Network analysis with {igraph}](http://www.gipsa-lab.grenoble-inp.fr/~sophie.achard/Tutorial_brainwaver/tutorial_practice_graph_html.html)

- [Visualization with {ggplot2}](https://privefl.github.io/R-presentation/ggplot2.html)

- [An introduction to R](https://github.com/fchuffar/intro_r)
